### 2021-10-15 README.Rmd
Update README.Rmd
release notes & docs

However, we know that data hosted at a given URL could change or disappear, and not all data we want to work with is available at a URL to begin with.  Digital Object Identifiers (DOIs) were created to deal with these problems of 'link rot'.  Unfortunately, there is no straight forward and general way to read data directly from a DOI, (which almost always resolves to a human-readable webpage rather than the data itself), often apply to collections of files rather than individual source we want to read in our script, and we must frequently work with data that does not (yet) have a DOI. Registering a DOI for a dataset has gotten easier through repositories with simple APIs like Zenodo and figshare, but this is still an involved process and still leaves us without a mechanism to directly access the data.

@@

```{r}
query_sources("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```

Note that `query_sources()` has found more locations than we have registered above.  This is because in addition to maintaining a local registry of sources, `contentid` registers online sources with the Hash Archive, `https://hash-archive.org`. (The Hash Archive doesn't store content, but only a list of public links at which content matching the hash has been seen.)  `query_sources()` has also checked for this content on the Software Heritage Archive, which does periodic crawls of all public content on GitHub which have also picked up a copy of this exact file. With each URL is a date at which it was last seen - repeated calls to `register()` will update this date, or lead to a source being deprecated for this content if the content it serves no longer matches the requested hash. We can view the history of all registrations of a given source using `query_history()`.

>>>>

However, we know that data hosted at a given URL could change or disappear, and not all data we want to work with is available at a URL to begin with.  Digital Object Identifiers (DOIs) were created to deal with these problems of 'link rot'.  Unfortunately, there is no straight forward and general way to read data directly from a DOI, (which almost always resolves to a human-readable webpage rather than the data itself), often apply to collections of files rather than individual source we want to read in our script, and we must frequently work with data that does not (yet) have a DOI. Registering a DOI for a dataset has gotten easier through repositories with simple APIs like Zenodo and figshare, but this is still an involved process and still leaves us without a mechanism to directly access the data.  For instance, the data referenced above has DOI <https://doi.org/10.3334/CDIAC/ATG.009>, but this is still not easy to work directly into our R scripts.

@@

```{r}
sources("hash://sha256/9412325831dab22aeebdd674b6eb53ba6b7bdd04bb99a4dbb21ddff646287e37")
```

Note that `sources()` has found more locations than we have registered above.  This is because in addition to maintaining a local registry of sources, `contentid` registers online sources with the Hash Archive, `https://hash-archive.org`. (The Hash Archive doesn't store content, but only a list of public links at which content matching the hash has been seen.)  `query_sources()` has also checked for this content on the Software Heritage Archive, which does periodic crawls of all public content on GitHub which have also picked up a copy of this exact file. With each URL is a date at which it was last seen - repeated calls to `register()` will update this date, or lead to a source being deprecated for this content if the content it serves no longer matches the requested hash. We can view the history of all registrations of a given source using `history_url()`.
